Community Data Science meets Digital Heritage: Controversies about World Heritage Sites in the Online Community of Wikipedia

### 2019-05-10 code/paper.Rmd
talk page length

@@

>>>>

wh_pages_talk_page_length <- 
left_join(page_data_for_all_pages,
          revision_history_page_details_wordcount)

ggplot(wh_pages_talk_page_length,
         aes(rh_n_edits,
             rh_revert_prop,
             label = str_wrap(Site, 30))) +
  geom_point(alpha = 0.5,
             aes(size =   (talk_page_wordcount),
                 colour = (talk_page_wordcount))) +
    geom_text_repel(
    data            = wh_pages_talk_page_length %>%  
                      filter(talk_page_wordcount > 8000),
    segment.size  = 0.2,
    colour = "black",
    force = 50,
    segment.color = "grey50",
    direction     = "both"
  ) +
  scale_y_log10() +
  scale_x_log10() +
  coord_fixed(1) +
  scale_color_viridis_c(name = "Talk page word count", 
                        labels = c(5000, 10000, 15000, 20000),
                        breaks = c(5000, 10000, 15000, 20000)) +
  scale_size_continuous(name = "Talk page word count", 
                        labels = c(5000, 10000, 15000, 20000),
                        breaks = c(5000, 10000, 15000, 20000)) +
   guides(color= guide_legend(), size=guide_legend()) +
  theme_minimal(base_size = 14) +
  labs(x = "Number of edits",
       y = "Proportion of edits that are reverts") +
    ggtitle("")

ggsave("figures/wh_wikpedia_pages_talk_page_wordcount_reverts_scatterplot.png")

@@

```{r}
```
